\begingroup 
\renewcommand{\section}[2]{\anonsection{Библиографический список}}
\begin{thebibliography}{00}

\bibitem{dbscan-alg}
    Martin Ester, Hans-Peter Kriegel, Jörg Sander, Xiaowei Xu.
    A density-based algorithm for discovering clusters in large spatial databases with noise // 
    Proceedings of the Second International Conference on Knowledge Discovery and Data Mining (KDD-96),
    AAAI Press, 
    1996.

\bibitem{conv-neoro}
    Convolutional Neural Networks (LeNet) 
    [Электронный ресурс] // 
    DeepLearning 0.1 documentation: [сайт]. 
    URL: http://deeplearning.net/tutorial/lenet.html 
    (дата обращения: 19.05.2019).

\bibitem{median-linear}
    Michael Cohen, Yin Tat Lee, Gary Miller, Jakub Pachocki, Aaron Sidford. 
    Geometric median in nearly linear time // 
    Proc. 48th Symposium on Theory of Computing (STOC 2016). — Association for Computing Machinery, 
    2016.

\bibitem{imagenet-challenge}
    Russakovsky O., Deng J., Su H., Krause J., Satheesh S., Ma S., Huang Z., Karpathy A., Khosla A., Bernstein M., Berg A.C., Fei-Fei. L. 
    ImageNet Large Scale Visual Recognition Challenge // 
    IJCV, 
    2015.

\bibitem{transfer-learning}
    Lin Y.P., Jung T.P.
    Improving EEG-Based Emotion Classification Using Conditional Transfer Learning //
    Frontiers in Human Neuroscience, 
    Jun 2017.

\bibitem{k-graph}
    D. Eppstein, M. S. Paterson, Frances Yao. 
    On nearest-neighbor graphs // 
    Discrete and Computational Geometry. 
    1997. — Т. 17, вып. 3. — С. 263–282.

\bibitem{java-doc}
    JDK 11.
    [Электронный ресурс] // 
    openjdk.java.net: [сайт]. 
    URL: http://openjdk.java.net/projects/jdk/11/
    (дата обращения: 10.05.2019).

\bibitem{love}
    #love hashtag on instagram 
    [Электронный ресурс] // 
    Instagram: [сайт]. 
    URL: https://www.instagram.com/explore/tags/love/ 
    (дата обращения: 20.05.2019).

\bibitem{web20}
    O'Reilly T. What Is Web 2.0 // 
    O’Reilly Media. 
    2005. 
    URL: https://www.oreilly.com/pub/a/web2/archive/what-is-web-20.html 
    (дата обращения: 20.05.2019).

\bibitem{postgresql-doc}
    PostgreSQL 11.3 Documentation
    [Электронный ресурс] // 
    PostgreSQL 11.3 Documentation: [сайт]. 
    http://www.postgresql.org/docs/current/interactive/
    (дата обращения: 10.05.2019).

\bibitem{spring-book}
    Ю. Козмина, Р. Харроп, К. Шефер, К. Хо. 
    Spring 5 для профессионалов //
    «Вильямс», 
    2019.

\bibitem{vgg16alg}
    Simonyan K., Zisserman A. 
    Very Deep Convolutional Networks for Large-Scale Image Recognition // 
    Computer Vision and Pattern Recognition, 
    Apr 2015.

\bibitem{deeplearning4j-book}
    Паттерсон Дж., Гибсон А. 
    Глубокое обучение с точки зрения практика //
    ДМК-Пресс, 
    2018.

\end{thebibliography}
\endgroup

\clearpage